Hot and fresh: Pervasive climate stressors of seagrass in a large Gulf coast estuary

### 2023-09-20 manu-draft.qmd
hillsborough flow temp plot

>>>>

![Relationship between water temperature and discharge in the Hillsborough River (USGS gage 02303000) over time.  The relationship is shown for February (dry month) and August (wet month) grouped by historic (1975-1999) and contemporary (2000-2022) time periods.  Regression lines with 95% confidence intervals for each temporal grouping are shown.](figs/flowtemp.png){#fig-flowtemp}
